\tool: Programmable, Efficient, and Scalable Secure Two-Party Computation

### 2017-10-27 OaklandSubmission/main.tex
security

\maketitle
\begin{abstract}
Secure two-party computation (\mpc) allows two mutually distrusting parties to compute any function on their joint inputs, without revealing anything other than the output of the function to one another. While the application and potential impact of secure computation is virtually limitless, writing an efficient and scalable secure protocol is by no means an easy feat. Prior work in designing such protocols, suffered from either a) a lack of programmability (e.g. requiring the programmer to write cryptography-aware circuits for the computation); b) a lack of efficiency for several natural computations (such as machine learning applications); or c) required cryptographers to design hand-crafted protocols for various applications. In this work, we present \tool: a new ``cryptographic-cost aware'' \mpc framework that generates efficient and scalable \mpc protocols from high-level programs that contain absolutely no cryptographic details. Programs in our language are easy-to-write, with lines of code that are comparable to their insecure implementations. Furthermore, the \mpc protocols generated by our framework outperform or match almost all recent works on hand-crafted secure two-party computation protocols (sometimes up to a 19x factor!).
\end{abstract}
\IEEEpeerreviewmaketitle

@@

\input{ex}
\input{ld}
\input{pipe}
\input{impl}

>>>>

\maketitle
% \begin{abstract}
% The abstract goes here.
% \end{abstract}
\IEEEpeerreviewmaketitle

@@

\input{ex}
\input{ld}
\input{security}
\input{pipe}
\input{impl}
